A fully labelled proof system for intuitionistic modal logics

### 2020-09-30 FullyLabelled/JLC/introduction.tex
fixed reference

Standard labelled sequent calculi for logics with
standard Kripke semantics attach to every formla $\fm A$ a label
$\lb x$, witten as $\labels xA$, and additionally use
\emph{relational atoms} of the form $\accs xy$ where 
the binary relation symbol $\rel$
%These calculi work best for logics with
%standard Kripke semantics, as in this case the relation $\rel$ 
is used to encode the accessibility relation in the Kripke models, such that
frame conditions corresponding to the desired logic can be directly
encoded as inference rules.
%\todo{Reviewer 1 complained about the ``best''}
Prominent examples are classical modal
logics and intuitionistic propositional logic, e.g., the frame
condition of transitivity ($\forall \lb {xyz}.\:\accs xy\AND \accs yz\IMP\accs xz$) can be translated into the
inference rule
\begin{equation}
\label{eq:Rtrans}
\vlinf{\rn{trans}}{}{\B, \accs xy, \accs yz, \Left \SEQ \Right}{
	\B, \accs xy, \accs yz, \accs xz, \Left \SEQ \Right}
\end{equation}
where $\B$ stands for a set of relational atoms, and $\Gamma$ and
$\Delta$ for multi-sets of labelled formulas~\cite{negri:vonplato:01}.\lutz{right ref?}

>>>>

Standard labelled sequent calculi for logics with
standard Kripke semantics attach to every formla $\fm A$ a label
$\lb x$, witten as $\labels xA$, and additionally use
\emph{relational atoms} of the form $\accs xy$ where 
the binary relation symbol $\rel$
%These calculi work best for logics with
%standard Kripke semantics, as in this case the relation $\rel$ 
is used to encode the accessibility relation in the Kripke models, such that
frame conditions corresponding to the desired logic can be directly
encoded as inference rules.
%\todo{Reviewer 1 complained about the ``best''}
Prominent examples are classical modal
logics and intuitionistic propositional logic, e.g., the frame
condition of transitivity ($\forall \lb {xyz}.\:\accs xy\AND \accs yz\IMP\accs xz$) can be translated into the
inference rule
\begin{equation}
\label{eq:Rtrans}
\vlinf{\rn{trans}}{}{\B, \accs xy, \accs yz, \Left \SEQ \Right}{
	\B, \accs xy, \accs yz, \accs xz, \Left \SEQ \Right}
\end{equation}
where $\B$ stands for a set of relational atoms, and $\Gamma$ and
$\Delta$ for multi-sets of labelled formulas~\cite{negri:jpl2005}.
